\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-07-24 manuscript.Rnw
Modify R style

<<preliminaries, echo=FALSE, results="hide">>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
set.seed(102)
@

@@

<<tmat>>=
tmat <- rbind(
  c(NA, 1, 2),
  c(NA, NA, 3),
  c(NA, NA, NA)
)
colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
tmat
@

@@

<<hesim_data>>=
library("hesim")
library("data.table")
n_patients <- 1000
patients <- data.table(
  patient_id = 1:n_patients,
  age = rnorm(n_patients, mean = 45, sd = 7),
  female = rbinom(n_patients, size = 1, prob = .51)
)

states <- data.table(
  state_id = c(1, 2),
  state_name = c("Stable", "Progression") 
)

strategies <- data.table(
  strategy_id = 1:3,
  strategy_name = c("SOC", "New 1", "New 2"),
  soc = c(1, 0, 0),
  new1 = c(0, 1, 0),
  new2 = c(0, 0, 1)
)

hesim_dat <- hesim_data(
  strategies = strategies,
  patients = patients,
  states = states
)
hesim_dat
@

@@

<<ictstm_utility>>=
utility_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(.8, .6),
             se = c(0.02, .05)
  ),
  dist = "beta")
utility_tbl
@

@@

<<ictstm_medcosts>>=
medcost_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(2000, 9500),
             se = c(2000, 9500)
  ),
  dist = "gamma")
medcost_tbl
@

@@

<<ictstm_drugcost_setup, echo=FALSE, results="hide">>=
n_times <- 2
n_states <- nrow(states)
n_strategies <- nrow(strategies)
n_i <- n_states * n_times
drugcost_dt <-  data.table(
    strategy_id = rep(strategies$strategy_id, each = n_i),
    state_id = rep(rep(states$state_id, each = n_times), n_strategies),
    time_start = rep(c(0, 3/12), n_states * n_strategies),
    est = c(2000, 2000, 1500, 1200,
           12000, 12000, 1500, 1200,
           15000, 15000, 1500, 1200)
) 
@

<<ictstm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt,
  dist = "fixed")
drugcost_tbl
@

@@

<<psm_fits_soc>>=
onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
fit_pfs_soc_wei <- flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female,
  data = onc_pfs_os_soc,
  dist = "weibull")

fit_os_soc_wei <- flexsurvreg(
  Surv(os_time, os_status) ~  female,
  data = onc_pfs_os_soc,
  dist = "weibull")

psmfit_soc_wei <- partsurvfit(
  flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei),
  data = onc_pfs_os_soc
)
@

@@

# Fit models
fit_pfs_wei <- flexsurv::flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female + new1 + new2,
  data = onc_pfs_os,
  dist = "weibull")

fit_os_wei <- flexsurvreg(
  Surv(os_time, os_status) ~ female + new1 + new2,
  data = onc_pfs_os,
  dist = "weibull")

@@

<<psm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt[time_start ==  0][, time_start := NULL],
  dist = "fixed")
drugcost_tbl
@

@@

<<psm_plot_survival, fig.show = "hide">>=
autoplot(psm$survival_, 
         labels = c(labs_cohort,
                    list(curve = c("PFS" = 1, "OS" = 2))
                    ),
         ci = TRUE, ci_style = "ribbon")
@

@@

<<cdtstm_params>>=
params_rr <- list(
  lrr_12_est = c(soc = log(1), new1 = log(.80), new2 = log(.71)),
  lrr_12_se = c(soc = 0, new1 = .03, new2 = .04),
  lrr_13_est = c(soc = log(1), new1 = log(.90), new2 = log(.85)),
  lrr_13_se = c(soc = 0, new1 = .02, new2 = .03)
)

params_rr_def <- define_rng({
  list(
    rr_12 = lognormal_rng(lrr_12_est, lrr_12_se),
    rr_13 = lognormal_rng(lrr_13_est, lrr_13_se)
  )}, n = n_samples)
params_rr_rng <- eval_rng(params_rr_def, params_rr)
@

@@

<<rr>>=
x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
rr <- cbind(xbeta(x_rr, params_rr_rng$rr_12),
            xbeta(x_rr, params_rr_rng$rr_13))
head(rr) 
@

>>>>

<<preliminaries, echo=FALSE, results="hide">>=
options(prompt = "R> ", continue = "+  ", width = 76, useFancyQuotes = FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
set.seed(102)
@

@@

<<tmat>>=
tmat <- rbind(c(NA, 1, 2), c(NA, NA, 3), c(NA, NA, NA))
colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
tmat
@

@@

<<hesim_data>>=
library("hesim")
library("data.table")
n_patients <- 1000
patients <- data.table(
  patient_id = 1:n_patients,
  age = rnorm(n_patients, mean = 45, sd = 7),
  female = rbinom(n_patients, size = 1, prob = .51)
)
states <- data.table(
  state_id = c(1, 2),
  state_name = c("Stable", "Progression") 
)
strategies <- data.table(
  strategy_id = 1:3,
  strategy_name = c("SOC", "New 1", "New 2"),
  soc = c(1, 0, 0),
  new1 = c(0, 1, 0),
  new2 = c(0, 0, 1)
)
hesim_dat <- hesim_data(
  strategies = strategies,
  patients = patients,
  states = states
)
hesim_dat
@

@@

<<ictstm_utility>>=
utility_tbl <- stateval_tbl(
  data.table(
    state_id = states$state_id,
    mean = c(.8, .6),
    se = c(0.02, .05)
  ),
  dist = "beta"
)
utility_tbl
@

@@

<<ictstm_medcosts>>=
medcost_tbl <- stateval_tbl(
  data.table(
    state_id = states$state_id,
    mean = c(2000, 9500),
    se = c(2000, 9500)
  ),
  dist = "gamma"
)
medcost_tbl
@

@@

<<ictstm_drugcost_setup, echo=FALSE, results="hide">>=
n_times <- 2
n_states <- nrow(states)
n_strategies <- nrow(strategies)
n_i <- n_states * n_times
drugcost_dt <-  data.table(
  strategy_id = rep(strategies$strategy_id, each = n_i),
  state_id = rep(rep(states$state_id, each = n_times), n_strategies),
  time_start = rep(c(0, 3/12), n_states * n_strategies),
  est = c(
    2000, 2000, 1500, 1200,
    12000, 12000, 1500, 1200,
    15000, 15000, 1500, 1200
  )
) 
@

<<ictstm_drugcost>>=
drugcost_tbl <- stateval_tbl(drugcost_dt, dist = "fixed")
drugcost_tbl
@

@@

<<psm_fits_soc>>=
onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
fit_pfs_soc_wei <- flexsurvreg(Surv(pfs_time, pfs_status) ~ female,
  data = onc_pfs_os_soc, dist = "weibull")
fit_os_soc_wei <- flexsurvreg(Surv(os_time, os_status) ~  female,
  data = onc_pfs_os_soc, dist = "weibull")
psmfit_soc_wei <- partsurvfit(
  flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei), 
  data = onc_pfs_os_soc)
@

@@

# Fit models
fit_pfs_wei <- flexsurvreg(Surv(pfs_time, pfs_status) ~ female + new1 + new2,
  data = onc_pfs_os, dist = "weibull")

fit_os_wei <- flexsurvreg(Surv(os_time, os_status) ~ female + new1 + new2,
  data = onc_pfs_os, dist = "weibull")

@@

<<psm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt[time_start ==  0][, time_start := NULL],
  dist = "fixed"
)
drugcost_tbl
@

@@

<<psm_plot_survival, fig.show = "hide">>=
autoplot(psm$survival_, 
  labels = c(labs_cohort, list(curve = c("PFS" = 1, "OS" = 2))),
  ci = TRUE, ci_style = "ribbon")
@

@@

<<cdtstm_params>>=
params_rr <- list(
  lrr_12_est = c(soc = log(1), new1 = log(.80), new2 = log(.71)),
  lrr_12_se = c(soc = 0, new1 = .03, new2 = .04),
  lrr_13_est = c(soc = log(1), new1 = log(.90), new2 = log(.85)),
  lrr_13_se = c(soc = 0, new1 = .02, new2 = .03)
)  
params_rr_def <- define_rng({
  list(
    rr_12 = lognormal_rng(lrr_12_est, lrr_12_se),
    rr_13 = lognormal_rng(lrr_13_est, lrr_13_se)
  )}, 
  n = n_samples
)
params_rr_rng <- eval_rng(params_rr_def, params_rr)
@

@@

<<rr>>=
x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
rr <- cbind(
  xbeta(x_rr, params_rr_rng$rr_12),
  xbeta(x_rr, params_rr_rng$rr_13)
)
head(rr) 
@
